Rmarkdown Features

### 2018-05-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: "`r Sys.Date()`"
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---

@@

```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---
```

@@

@@

\usepackage{multicol}
\usepackage{bm}

@@

%設定中英文的字型
%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
\setCJKmainfont{蘋方-繁}

@@

### Rounded Edge
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
```
![Bootstrap Rounded](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}

### Circle Image
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
```
![Bootstrap Circle](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}

### Thumbnail
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
```
![Bootstrap Thumbnail](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}

>>>>

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---

@@

```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---
```

@@

Note that Latex only accepts fontsize of 10pt, 11pt, or 12pt. See [this](https://github.com/rstudio/rmarkdown/issues/878) for more detail.

@@

\usepackage[fontsize=13pt]{scrextend}

@@

%設定中英文的字型
%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
% AR PL KaitiM Big5 標楷體
% .PingFang TC
% Noto Sans CJK TC
\setCJKmainfont{AR PL KaitiM Big5}

@@

### Rounded Edge
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
```
![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}

### Circle Image
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
```
![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}

### Thumbnail
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
```
![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
